\documentclass{article}
% ------------------------------------------------------- 
% MARGINS
% ------------------------------------------------------- 
\usepackage[
	a4paper,        % Paper size
	top=5cm,      % Top margin
	bottom=2cm,   % Bottom margin
	left=1cm,     % Left margin
	right=1.5cm,    % Right margin
%	showframe       % Uncomment to show frames around the margins for debugging
]{geometry}

% ------------------------------------------------------- 
% FONTS
% ------------------------------------------------------- 
\usepackage[scaled=0.8]{librebaskerville}
\usepackage{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\baselinestretch}{1.5} 

% ------------------------------------------------------- 
% COLOURS
% ------------------------------------------------------- 
\usepackage[dvipsnames]{xcolor}
\definecolor{TitleGrey}{HTML}{656A6E}
\definecolor{BodyGrey}{HTML}{3A4553}
\definecolor{LightGrey}{HTML}{B6B6B6}

% ------------------------------------------------------- 
% COLUMNS 
% ------------------------------------------------------- 
\usepackage{paracol}                  % Multicolumn
\columnratio{0.2, 0.8}                % Column ratio
\setlength\columnsep{0.06\textwidth}  % Amount of horizontal space between the columns

% FONTAWESOME
\usepackage{fontawesome}

\usepackage[none]{hyphenat}

% ------------------------------------------------------- 
% MAKETITLE
% ------------------------------------------------------- 
\usepackage{titling}
\renewcommand{\maketitle}{
  {\noindent\rmfamily\huge\bfseries\MakeUppercase\theauthor}

  {\color{black}\rmfamily\normalsize\bfseries{Backend Engineer}}
}

% ------------------------------------------------------- 
% CONTACT DETAILS
% ------------------------------------------------------- 
\newcommand{\contacts}[3]{
  {
    {\noindent\rmfamily\small\color{BodyGrey}\bfseries{\color{LightGrey}\faPhone}\hspace{3pt}#1}

    {\noindent\rmfamily\small\color{BodyGrey}\bfseries{\color{LightGrey}\faEnvelope}\hspace{3pt}#2}

    {\noindent\rmfamily\small\color{BodyGrey}\bfseries{\color{LightGrey}\faLink}\hspace{3pt}#3}

  }
}

% ------------------------------------------------------- 
% SECTION TITLES 
% ------------------------------------------------------- 
\usepackage{titlesec}
\titleformat{\section}
{\color{TitleGrey}\rmfamily\small\bfseries\uppercase}{}{0em}{}
[\titlerule]

% -------------------------------------------------------------------------------------------------------------- 
% DOCUMENT
% --------------------------------------------------------------------------------------------------------------
\begin{document}
\pagenumbering{gobble}
  \title{CV}
  \author{Kunhee Ha}
% ------------------------------------------------------- 
% LEFT COLUMN
% ------------------------------------------------------- 
\begin{paracol}{2}
  \raggedright
  \maketitle

% ------------------------------------------------------- 
% CONTACT DETAILS
% ------------------------------------------------------- 
\section{Contact}

\contacts
  {07947513711}
  {kunheeha@gmail.com}
  {kunheeha.com}

% ------------------------------------------------------- 
% RIGHT COLUMN
% ------------------------------------------------------- 
  \switchcolumn
  \vspace{3pt}
\color{BodyGrey}
Dear Hiring Manager,
\vspace{15pt}

I am writing to express my keen interest in the Backend Engineer position at Sano Genetics, where I can combine my experience in Python development with SQLAlchemy from my previous role, and background knowledge on bioinformatics and genomics from my undergraduate degree to contribute to your groundbreaking work in personalised medicine research. 
\vspace{15pt}


In my previous role as a junior developer at Juno, I leveraged Python and SQLAlchemy to build a standalone tool that analysed legal letters and stored relevant information in a Postgres database, providing invaluable insights to legal teams. This experience honed my skills in developing robust solutions and integrating them with database systems. Additionally, my main duties involved working on Juno's in-house web application built on a Flask backend and reviewing pull requests from my peers. This allowed me to strengthen my skills in writing tests for implementations and maintaining code quality.
\vspace{15pt}


While my professional experience spans over a year, I acknowledge that my exposure has been primarily within the legal technology domain. However, I gained a solid foundation in bioinformatics and genomics during my undergraduate studies in biochemistry, and believe this background will allow me to adapt quickly in understanding the intricacies in business needs and applying it effectively during planning and implementation in the software development context.
\vspace{15pt}


Thank you for considering my application. I am confident that my multidisciplinary background and previous experience, coupled with my keen interest in the intersection of bioinformatics and technology make me an excellent fit for a Backend Engineer role at Sano. I look forward to the opportunity to contribute to Sano's mission and be a part of a team dedicated to transforming the future of personalised medicine research.
\vspace{15pt}


Sincerely,

Kunhee Ha
\end{paracol}
\end{document}
