% ------------------------------------------------------- 
% TODO
% ------------------------------------------------------- 
% [x] Group packages and options for better navigation
% [x] Add heading comments
% [ ] Add comments per line for easy navigation and grep
% [ ] Maybe I should make a separate .cls for all the config
% [ ] Change everything into functions

\documentclass{article}

% ------------------------------------------------------- 
% MISC
% ------------------------------------------------------- 
\usepackage{titling}
\usepackage{enumitem}         % bullet points no left margin
%\usepackage[none]{hyphenat}  % don't hyphenate anything
\usepackage{hyperref}         % links

% ------------------------------------------------------- 
% MARGINS
% ------------------------------------------------------- 
\usepackage[
	a4paper,        % Paper size
	top=1.5cm,      % Top margin
	bottom=1.5cm,   % Bottom margin
	left=1.5cm,     % Left margin
	right=1.5cm,    % Right margin
%	showframe       % Uncomment to show frames around the margins for debugging
]{geometry}


% ------------------------------------------------------- 
% COLUMNS 
% ------------------------------------------------------- 
\usepackage{paracol}                  % Multicolumn
\columnratio{0.5, 0.5}                % Column ratio
\setlength\columnsep{0.16\textwidth}  % Amount of horizontal space between the columns


% ------------------------------------------------------- 
% FONTS
% ------------------------------------------------------- 
\usepackage[scaled=0.8]{librebaskerville}
\usepackage[scaled=0.8]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}


% ------------------------------------------------------- 
% COLOURS
% ------------------------------------------------------- 
\usepackage[dvipsnames]{xcolor}
\definecolor{TitleGrey}{HTML}{656A6E}
\definecolor{BodyGrey}{HTML}{3A4553}
\definecolor{MyBlue}{HTML}{1E55B0}
\definecolor{LightGrey}{HTML}{B6B6B6}


% FONTAWESOME
\usepackage{fontawesome}

% ------------------------------------------------------- 
% MAKETITLE
% ------------------------------------------------------- 
\renewcommand{\maketitle}{
  {\noindent\rmfamily\Huge\bfseries\MakeUppercase\theauthor}
  \vspace{.8em}
  }


% ------------------------------------------------------- 
% CONTACT DETAILS
% ------------------------------------------------------- 
\newcommand{\contacts}[5]{
  {\noindent\rmfamily\small\color{BodyGrey}\bfseries
    {\color{LightGrey}\faPhone}\hspace{5pt}#1\hspace{12pt}      % Phone
    {\color{LightGrey}\faEnvelope}\hspace{5pt}#2\hspace{12pt}   % Email
    {\color{LightGrey}\faLink}\hspace{5pt}#3\hspace{12pt}       % Website
    {\color{LightGrey}\faGithub}\hspace{5pt}#4\hspace{12pt}     % Github
    {\color{LightGrey}\faGithub}\hspace{5pt}#5                  % Github Work
  }
}


% ------------------------------------------------------- 
% SECTION TITLES 
% ------------------------------------------------------- 
\usepackage{titlesec}
\titleformat{\section}
{\color{TitleGrey}\rmfamily\normalsize\bfseries\uppercase}{}{0em}{}
[\titlerule]

\titleformat{\subsection}
{\color{black}\rmfamily\large\bfseries}{}{0em}{}
\titlespacing{\subsection}{0pt}{1em}{0.2em}

\titleformat{\subsubsection}[runin]
{\color{MyBlue}\rmfamily\bfseries}{}{0em}{}


% ------------------------------------------------------- 
% SKILLS SECTION
% ------------------------------------------------------- 
\usepackage{soul}       % Underline config
\usepackage{setspace}   % Spacing
\setul{1.2ex}{0.2ex}
\newcommand{\skill}[2][LightGrey]{\color{black}\setulcolor{#1}\ul{~~~#2~~~}\hspace{5pt}}


% -------------------------------------------------------------------------------------------------------------- 
% DOCUMENT
% --------------------------------------------------------------------------------------------------------------
\begin{document}
\pagenumbering{gobble}

% ------------------------------------------------------- 
% MAKETITLE
% ------------------------------------------------------- 
  \title{CV}
  \author{Kunhee Ha}

  \maketitle

% ------------------------------------------------------- 
% CONTACT DETAILS
% ------------------------------------------------------- 
\contacts
  {07947513711}
  {kunheeha@gmail.com}
  {kunheeha.com}
  {github.com/kunheeha}
  {github.com/kunheeha-bloom}

\color{BodyGrey}
% ------------------------------------------------------- 
% Summary
% ------------------------------------------------------- 
\section{Summary}
Backend Engineer currently working in fintech, specialising in building microservices for open banking integrations in Go. Recently spearheaded the end-to-end design and deployment of an open banking data integration project, while ensuring system reliability and adhering to regulatory compliance. Previously worked on automation of legal processes in conveyancing. Committed to continuous learning, as demonstrated by pursuing postgraduate modules in Computer Science and AI alongside full-time employment, applying insights from its undertaking to real-world challenges.
  \raggedright
  \vspace{3pt}
  % ------------------------------------------------------- 
  % Experience
  % ------------------------------------------------------- 
  % ------------------------------------------------------- 
  % Bloom
  % ------------------------------------------------------- 
  \section{Experience}
  \subsection{Backend Engineer}
  \subsubsection{Bloom}
  {\color{LightGrey}\scriptsize\href{https://www.bloommoney.co}{\faExternalLink}}
  {\color{TitleGrey}{\small a fintech company that provides a digitised ROSCA as a service.}}
  \hspace*{\fill}{\color{TitleGrey}{\scriptsize\faCalendar}\hspace{5pt}{\small09/2023 -- 06/2025}}

  \begin{itemize}[leftmargin=*]
    \setlength\itemsep{-2pt}
    \item Spearheaded the design, development, and deployment of an open banking data integration project, ensuring high system reliability and full regulatory compliance.
    \item Implemented robust encryption mechanisms for storing customers' open banking data, including a dedicated service to manage key rotations for enhanced security.
    \item Built a customer address lookup service to migrate away from a third-party provider, improving performance.
    \item Collaborated with the front-end developer to ensure a seamless customer authentication flow, enabling users to connect their bank accounts securely to the open banking service.
  \end{itemize}

  % ------------------------------------------------------- 
  % Juno
  % ------------------------------------------------------- 
  \subsection{Junior Developer}
  \subsubsection{Juno}
  {\color{LightGrey}\scriptsize\href{https://www.juno.legal}{\faExternalLink}}
  {\color{TitleGrey}{\small a law firm that uses an in-house proprietary case management system to automate aspects of conveyancing.}}
  \hspace*{\fill}{\color{TitleGrey}{\scriptsize\faCalendar}\hspace{5pt}{\small10/2021 -- 12/2022}}
  
  \begin{itemize}[leftmargin=*]
    \setlength\itemsep{-2pt}
    \item Developed and implemented automation solutions to repetitive legal processes in the domain of conveyancing, increasing operational efficiency and mitigating human errors, reducing conveyancing time by eight weeks compared to national average. {\color{LightGrey}\scriptsize\href{https://www.juno.legal/information/how-long-does-conveyancing-take/}{\faExternalLink}}
    \item Built internal tool to parse and analyse legal documents, specifically requisition letters from HM Land Registry, designed and implemented the database schema and data hydration process to store extracted data.
    \item Successfully integrated bespoke workflows for two new company clients and a mortgage lender, helping establish key partnerships and expanding the platform's capabilities.
    \item Collaborated with the legal team to understand domain-specific requirements and deliver tailored solutions.
  \end{itemize}

  % ------------------------------------------------------- 
  % Education
  % ------------------------------------------------------- 
  \section{Education}
  \subsection{PGCert Computer Science and Artificial Intelligence}
  \subsubsection{University of York}
  \hspace*{\fill}{\small Awarded 2023}
  \begin{itemize}[leftmargin=*]
    \setlength\itemsep{-2pt}
    \item Achieved a mark of 91\% in algorithms and data structures exam, demonstrating a strong understanding of core concepts.
    \item Demonstrated proficiency in Java through comprehensive coursework.
  \end{itemize}

  \subsection{BSc Biochemistry (Hons.)}
  \subsubsection{University of Birmingham}
  \hspace*{\fill}{\small Graduated 2019}
  \begin{itemize}[leftmargin=*]
    \setlength\itemsep{-2pt}
    \item Developed expertise in data interpretation using R, enabling effective statistical analysis and data visualisation.
    \item Conducted multiple laboratory projects in which novel data was collected and interpreted with R.
  \end{itemize}
  % ------------------------------------------------------- 
  % Skills
  % ------------------------------------------------------- 
  \section{Skills}
  \titleformat{\subsection}[runin]
  {\color{MyBlue}\rmfamily\bfseries}{}{0em}{}

  \subsection{Languages}
    \hspace*{\fill}
    \skill{Go}
    \skill{Python}
    \skill{Java}
    \skill{Javascript}
    \skill{Bash}
    \skill{SQL}
  \subsection{Databases/Cache}
    \hspace*{\fill}
    \skill{CockroachDB}
    \skill{PostgreSQL}
    \skill{Redis}
    \skill{SQLite}
  \subsection{DevOps/Deployment}
    \hspace*{\fill}
    \skill{Docker}
    \skill{Kubernetes}
    \skill{AWS (EC2, ECR, ECS, EKS)}
    \skill{NGINX}
    \skill{Gunicorn}
  \subsection{Frameworks/Libraries}
    \hspace*{\fill}
    \skill{GORM}
    \skill{Flask}
    \skill{Django}
    \skill{Alembic}
    \skill{SQLAlchemy}
  \subsection{Markup/Stylesheet}
    \hspace*{\fill}
    \skill{{\rmfamily\LaTeX}}
    \skill{Markdown}
    \skill{HTML}
    \skill{CSS}
  %\subsection{Version Control}
  %  \skill{Git}
\end{document}
